\documentclass{article}
\begin{document}
% Nice general title for now...
\textbf{Syllabus:} Logic in Computer Science

\section*{Course Description}
This course offers a graduate-level survey of the different applications of logic in computer science,
including programming language design, model checking, interactive and automatic theorem proving and their use in algorithms.

\section*{Grading}
\begin{itemize}
\item Reading Summaries: 20\%
\item 4 Programming Assignments: 50\%
\item 1 Final Project: 30\%
\end{itemize}

\section*{Programming Assignments}
\begin{itemize}
\item 
\textbf{Programming Language Theory+Implementation:}
Implement chosen parts of an interpreter and then compiler for a toy imperative programming language:
\begin{itemize}
\item Implement structural operational semantics as given in lecture/handout.
\item Implement type checker for simple type system that rules accesses to undefined variables.
\item Implement dead-code elimination (requires implementing free/bound variables)
\item Add garbage-collected data structures (garbage collector provided by language runtime and/or us)
\item Implement LLVM translation (LLVM starter code + garbage collector provided by us).
\end{itemize}
 
 \item
 \textbf{Implementation-Level Software Model-Checking}
 \begin{itemize}
  \item Reuses language of previous assignment both for the language-being-checked and to express propositions.
  \item Version 1: Given P:bool, Q:bool, e:stmt where e has finite state, model-check the Hoare triple {P}e{Q}.
  \item Version 2: Symbolically model-check {P}e{Q} (we provide interface to SMT solver). This reuses the semantics of the language from the previous assignment.
  \item Version 3: Counter-Example-Guided Abstraction Refinement 
  \item Other options: Write your own SAT solver, write your own BDD implementation.
 \end{itemize}
 
 \item
 \textbf{Forward-Chaining Logic Programming}
 \begin{itemize}
 \item Implement Datalog interpreter using semantics given in class.
 \item Test case (provided): interpreter for imperative language.
 \item Write small database application.
 \item Solve some cute algorithms problem.
 \item Parallelize Datalog interpreter.???
 \item Written: Correctness proofs for logic programs???
 \end{itemize}

 \item
 \textbf{Certifying Compilation}
 \begin{itemize}
 \item Formalize refinement logic over imperative programs in Isabelle/HOL, including some rules for dead code elimination (and other optimizations if time - common subexpression elimination?).
 \item Augment compiler to produce refinement proofs, which the starter code then helps export to Isabelle/HOL.
 \item Run the exported Isabelle code with your formalization, and viola you have a certifying compiler!
 \end{itemize}

 
%  \item
% \textbf{}
% \begin{itemize}
% \item
% \end{itemize}

\end{itemize}


\section*{Lectures}
\begin{enumerate}
\item Overview (Please Don't Drop The Class)
% Unit 1: Programming Language Semantics
\item Structural Operational Semantics
\item Well-Typed Imperative Programs
\item Safety for Imperative Programs
\item Axiomatics for Program Equivalence
\item Axiomatics II: Axiomatic Compilation into SSA
\item Implementation: LLVM and Garbage Collection.
\item Denotational Semantics: Justifying Equivalence
\item Hoare Logic: Verifying on Paper
% Unit 2: Model Checking
\item Finite-State Model-Checking: Verifying with Semantics
\item Programming with Satisifiability (NP-Complete Problems, Symbolic Execution) 
\item Symbolic Model-Checking
\item CEGAR
\item Model-Checking Temporal Logic
\item SMT Solving with BDDs. Maybe also arithmetic solving for reals and integers.
% Unit 3: Logic Programming
\item Programming with Axioms: Datalog
\item Datalog Implementation 
\item Higher-Order Logic Programs: An Interpreter in Datalog
\item Correctness of Logic Programs
% Unit 4: Interactive Theorem-Proving
\item Isabelle/HOL: Verifying a Logic Program
\item Isabelle/HOL: Certifying Safety for Imperative Programs
\item Isabelle/HOL: Programming Compilers in Proof Assistants
\item Isabelle/HOL: Generalizing Hoare with Dynamic Logic
% Unit 5: Applications + Fun Stuff
\item Isabelle/HOL + KeYmaera X: Differential Dynamic Logic and CPS
\item Verificating the Tests: Next-Generation Airborne Collision-Avoidance System
\item Type Systems for Functional Languages + Curry-Howard
\item Frontiers in Semantics: Concurrency
\item Frontiers in Type Theory: New Foundations (Higher-Inductive Types)
\item Project Presentations
\end{enumerate}

%\begin{tabular}{c|c|c}
%Number & Topic & Deadline & Reading\\\hline
%1 &  & & \\

\end{document}